---
title: Untitled
format:
  dissertation-template-typst: default
---

```{r include = FALSE}
library(tidyverse)
library(flextable)
library(officer)

load('staged_results/chapter5/ch5_confirmatory_results.RData')
load('staged_results/chapter5/supp/staged_results.RData')
load('staged_results/chapter5/ch5_exploratory_results.RData')
load('staged_results/chapter5/ch5_fig6.RData')

# set up flextable for tables
set_flextable_defaults(
  font.family = "Times",
  font.size = 10,
  font.color = "black",
  line_spacing = 1,
  padding.bottom = 1,
  padding.top = 1,
  padding.left = 1,
  padding.right = 1
)

knitr::opts_chunk$set(
  echo = F,
  fig.align = "center",
  fig.pos = "!t", 
  out.extra = "",
  fig.show = "asis",
  message = FALSE,
  tab.topcaption = T,
  warning = FALSE
)
```

```{=typst}
#show: article.with(
  chapter: "Supplementary materials",
  chtitle: "Appendix 4"
)
```

```{=typst}
#pagebreak(to: "odd")
```

# Appendix 4 - Chapter 5

## Section 1. Pilot study

A total of 99 Dutch adolescents (mean age = `r ch5_pilot_demo$m_age`, SD = `r ch5_pilot_demo$sd_age`, range = [`r ch5_pilot_demo$min_age`, `r ch5_pilot_demo$max_age`]) participated in the Pilot study via Prolific.
The main goal of the Pilot study was to obtain feedback on the tasks (e.g., difficulty, clarity of instructions), and to explore bivariate correlations between the measures.
Participants completed the same tasks as in the main study: (1) Operation Span Task, (2) Rotation Span Task, and (3) Binding-Updating Task.
The Rotation Span Task was administered in a second session, and was completed by a subsample of 50 participants.
All three tasks followed the exact same procedure as in the main study.

In addition, participants completed measures of material deprivation, neighborhood threat, and unpredictability.
These measures differed from the more comprehensive measures used in the main study, and were included to obtain quick, descriptive estimates.
Material deprivation was measured using seven items about perceived level of available resources.
Unpredictability was measured using a scale of perceived unpredictability [@mittal_2015; @young_2018].
Neighborhood violence exposure was measured using the Neighborhood Violence Scale [NVS\; @frankenhuis_deVries_2020; @frankenhuis_2018] as well as two items measuring involvement in fights.
Participants responded to items of all questionnaires on a scale of 1 (never true) to 5 (very often true).
Finally, participants provided feedback on the difficulty of the tasks and the clarity of the task instructions.

Pilot data were collected sequentially to allow for intermediate changes to instructions based on participants' feedback.
The first session (including the Operation Span Task and the Binding-Updating Task) took approximately 35 minutes to complete, and participants were paid 5.25 GBP.
The second session (including the Rotation Span Task) took approximately 9 minutes to complete, and participants were paid 1.50 GBP.

Table A4.1 presents bivariate correlations among the WM tasks, and between the WM tasks and measures of adversity.
The WM tasks correlated moderately to strongly with each other.
The strongest correlation was between the Binding and Updating score (.80).
This is not surprising given that both scores are derived from the same task, and shows the importance of accounting for this association in the model.
Neither unpredictability nor material deprivation were significantly associated with performance on any of the WM tasks.
However, higher levels of experienced neighborhood threat were associated with lower performance on the Binding and Updating Task.
Note that these associations were based on raw task performance and not on latent estimates.

```{r}
#| tab.id: tableA4.1
#| results: markup
ch5_pilot_table1 |> 
  flextable::compose(
    i = 1, j = 1,
    as_paragraph(as_b("Table A4.1. "), "Bivariate correlations between WM tasks and adversity measures in the Pilot"),
    part = "header"
  ) |> 
  padding(
    i = 1:16,
    j = 1:8,
    padding.top = 3,
    padding.bottom = 3,
    part = "body"
  ) |> 
  padding(
    i = 1:2,
    j = 1:8,
    padding.top = 3,
    padding.bottom = 3,
    part = "header"
  ) |> 
  padding(
    i = 1,
    j = 1:8,
    padding.top = 3,
    padding.bottom = 3,
    part = "footer"
  ) |> 
  autofit()
```

## Section 2. Exploratory analyses

To contextualize our confirmatory (preregistered) findings, we conducted three exploratory (non-preregistered) analyses.
First, we explored associations between adversity and performance on the separate WM tasks using linear regression.
Second, we constrained regression paths in the SEM to zero, as an alternative to the equivalence tests.
Third, we computed Bayes Factors for the equivalence tests.

### Linear regression analyses

We estimated a total of five linear regression models, one per WM task.
Each model included the same independent variables and covariates as the primary analysis.
We adjusted for multiple testing across models involving the Rotation Span Task, Operation Span Task, and the binding trials of the Binding-Updating Task, and separately for the updating trials of the Binding-Updating Task, as the former three tasks are primarily conceptualized as WM capacity tasks.
We also tested for practical equivalence in the same way as for the confirmatory analyses

The results are summarized in Figure A4.1.
Threat was negatively associated with performance on the Rotation Span Task ($\beta$ = `r ch5_lm_reg_coef_expl |> filter(term == "threat_comp", task == "rspan") |> pull(estimate) |> formatC(digits = 2, width = 2, format = 'f')`, *p* = `r ch5_lm_reg_coef_expl |> filter(term == "threat_comp", task == "rspan") |> pull(pvalue_adj) |> formatC(digits = 3, width = 3, format = 'f') |> str_remove(string = _, pattern = "^0")`), Operation Span Task ($\beta$ = `r ch5_lm_reg_coef_expl |> filter(term == "threat_comp", task == "Ospan") |> pull(estimate) |> formatC(digits = 2, width = 2, format = 'f')`, *p* = `r ch5_lm_reg_coef_expl |> filter(term == "threat_comp", task == "Ospan") |> pull(pvalue_adj) |> formatC(digits = 3, width = 3, format = 'f') |> str_remove(string = _, pattern = "^0")`), and binding trials of the Binding-Updating Task ($\beta$ = `r ch5_lm_reg_coef_expl |> filter(term == "threat_comp", task == "binding") |> pull(estimate) |> formatC(digits = 2, width = 2, format = 'f')`, *p* = `r ch5_lm_reg_coef_expl |> filter(term == "threat_comp", task == "binding") |> pull(pvalue_adj) |> formatC(digits = 3, width = 3, format = 'f') |> str_remove(string = _, pattern = "^0")`).
Unpredictability in perceived scarcity was positively associated with performance on the Rotation Span Task ($\beta$ = `r ch5_lm_reg_coef_expl |> filter(term == "p_scar_cv", task == "rspan") |> pull(estimate) |> formatC(digits = 2, width = 2, format = 'f')`, *p* = `r ch5_lm_reg_coef_expl |> filter(term == "p_scar_cv", task == "rspan") |> pull(pvalue_adj) |> formatC(digits = 3, width = 3, format = 'f') |> str_remove(string = _, pattern = "^0")`).
None of the types of adversity were significantly associated with performance on the updating trials of the Binding-Updating Task.

In addition, there was some limited evidence for practical equivalence, especially for unpredictability in the income-to-needs ratio, which showed a practically equivalent association with the Operation Span Task, Rotation Span Task, and Updating Task.
We also found a practically equivalent association between unpredictability in perceived scarcity and the Binding Task.

```{r}
#| label: FigureA4.1
#| fig-width: 6.5
#| fig-height: 6
#| dpi: 600
#| out-width: 6in
#| fig-cap: | 
#|   **Figure A4.1.** Exploratory (non-preregistered) results testing the association between threat, deprivation, and unpredictability on residual variances of separate WM tasks. The gray area shows the area of practical equivalence. Solid points indicate effects outside the area of practical equivalence, which was true for all effects. Standard errors represent the 95% confidence intervals. CV = coefficient of variation; INR = income-to-needs ratio; M = mean; WM = working memory.
ch5_fig6
```

### Bayes Factors for equivalence tests

As a robustness check, we calculated Bayes factors for the preregistered equivalence tests using the *bain* package [@hoijtink_2019], in which we evaluated evidence in favor of the hypothesis that the effects fell within the equivalence bounds, relative to the hypothesis that the effects fell outside the equivalence bounds.
The results are summarized in Table A4.3.
For all but one association, the model comparisons showed at least strong evidence in favor of the hypothesis that the effects fell within the equivalence bounds (BF~10~ ranging between `r ch5_BF_expl04 |> filter(Hypothesis != '-0.1 < (WM capacity ~ Threat) < 0.1') |> pull(BF.c) |> min()` and `r ch5_BF_expl04 |> filter(Hypothesis != '-0.1 < (WM capacity ~ Threat) < 0.1') |> pull(BF.c) |> max()`.
The only exception was the association between threat and WM capacity, for which we found moderate evidence for the hypothesis that the effect fell within the equivalence bounds (BF~10~ = `r ch5_BF_expl04 |> filter(Hypothesis == '-0.1 < (WM capacity ~ Threat) < 0.1') |> pull(BF.c)`.
Thus, these results were inconsistent with the preregistered frequentist equivalent tests.
  
```{r}
#| tab.id: tableA4.3
#| results: markup
ch5_table_s3 <- ch5_BF_expl04 |> 
  select(Hypothesis, BF.c) |>
  flextable::flextable() |>
  compose(i = 1, j = 2, as_paragraph("BF", as_sub('10')), part = "header") %>%
  add_header_row(
    values = " ",
    colwidths = 2
  ) |> 
  flextable::compose(
    i = 1, j = 1, 
    as_paragraph(as_b("Table A4.3. "), "Bayes Factors for practical equivalence tests."),
    part = "header"
  ) |> 
  add_footer_row(
    values = " ",
    colwidths = 2
  ) |> 
  flextable::compose(
    i = 1, j = 1, 
    as_paragraph("BF = Bayes factor; CV = coefficient of variance, INR = income-to-needs ratio, M = mean, Perc. Scarcity = perceived scarcity, WM = working memory"), 
    part = "footer"
  ) |> 
  border_remove() |> 
  border(i = 1, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 10, border.bottom = fp_border_default(), part = "body") %>% 
  padding(
    i = 1:10,
    j = 1:2,
    padding.top = 3,
    padding.bottom = 3,
    part = "body"
  ) |> 
  padding(
    i = 1:2,
    j = 1:2,
    padding.top = 3,
    padding.bottom = 3,
    part = "header"
  ) |> 
  padding(
    i = 1,
    j = 1:2,
    padding.top = 3,
    padding.bottom = 3,
    part = "footer"
  ) |> 
  autofit()

ch5_table_s3
```

## Section 3. Histograms of independent measures

```{r}
#| label: FigureA4.2
#| fig-width: 6
#| fig-height: 4
#| dpi: 600
#| fig-cap: | 
#|   **Figure A4.2.** Histograms for mean perceived material deprivation over time.
ch5_p_scar_m_combn_hist
```

```{r}
#| label: FigureA4.3
#| fig-width: 6
#| fig-height: 4
#| dpi: 600
#| fig-cap: | 
#|   **Figure A4.3.** Histogram for the mean income-to-needs ratio over time.
ch5_p_scar_m_combn_hist
```

```{r}
#| label: FigureA4.4
#| fig-width: 6
#| fig-height: 4
#| dpi: 600
#| fig-cap: | 
#|   **Figure A4.4.** Histograms for mean threat exposure over time.
ch5_threat_combn_hist

```

```{r}
#| label: FigureA4.5
#| fig-width: 6
#| fig-height: 4
#| dpi: 600
#| fig-cap: | 
#|   **Figure A4.5.** Histograms for unpredictability in measures of perceived scarcity over time (coefficient of variation).
ch5_p_scar_cv_combn_hist
```

```{r}
#| label: FigureA4.6
#| fig-width: 4
#| fig-height: 2
#| dpi: 600
#| fig-cap: | 
#|   **Figure A4.6.** Histograms for unpredictability in the income-to-needs ratio over time (coefficient of variation).
ch5_inr_cv_hist
```

```{=typst}
#pagebreak()
```
